---
title: "Data Modeling - Snow_Survey"
author: "Melissa Widas"
date: "2024-04-09"
output: html_document
---

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)

snow <- read_csv(here("week1", "ASDN_Snow_survey.csv"))

colnames(snow)
```

```{r}
# CREATE TABLE ASDN_Snow_survey (
#     Site TEXT,
#       FOREIGN KEY (Site) References Site (Code)
#     Year INTEGER NOT NULL,
#     Date DATE NOT NULL,
#     Plot TEXT NOT NULL,
#     Location TEXT NOT NULL,
#     Snow_cover REAL NOT NULL,
#       CHECK (Snow_cover <= 100),
#     Water_cover REAL NOT NULL
#       CHECK (Water_cover <= 100),
#     Land_cover REAL NOT NULL
#       CHECK (Land_cover <= 100),
#     Total_cover REAL NOT NULL
#       CHECK (Total_cover = 100),
#     Observer TEXT NOT NULL,
#       FOREIGN KEY (Observer) References Personnel (Abbreviation)
#     Notes
# );
```

- Site is a foreign key for Site in the Code table
- Snow_cover needs to be a value that is at or below 100 as it is a percent
- Water_cover needs to be a value that is at or below 100 as it is a percent
- Land_cover needs to be a value that is at or below 100 as it is a percent
- Total_cover is the sum of Snow_cover, Water_cover, Land_cover and needs to equal 100 indicating 100 percent
- Observer is a foreign key for Abbreviation in the Personnel table
